\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-23 tex/paper.tex
Modified abstract and fixed width

%}}}
\begin{abstract}
This work presents a technique for incorporating Copy-on-Write in the development of a high level
system on top of an unaware persistent storage. The system in this case is a security management
system, but the technique and conclusions drawn are general enough to be applicable to any system
with vaguely similar consistency requirements. The scalability of the system is tested and the
technique is evaluated and the technique is shown to be very efficient (scalable to >
simultaneous users on a single node), but a better solution is also suggested in the
conclusion.\\

@@

After adding indices, the building of the project tree was able to finish 50 times faster and the
server was able to serve 2100 requests/s, see Listing~\ref{INDEXREQUEST}. If using the same
approximated average that was used in connection to Listing~\ref{TREEREQUEST} (30 requests/s), the
maximum number of clients that one node can handle will be >60000, without taking the web servers
limits or content posting into consideration.

@@

\subsection{Security of the system}
\subsubsection{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius 
is mainly focussed at being deployed in internal networks which usually has an LDAP service enabled. 
LDAP also makes it easier for the user to login as no separate account is needed for Perius and 
thus the user can use the same account as for all the LDAP connected services on the internal 
network.

@@

\subsubsection{Copy-on-Write's effect on Scalability}
As no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from how its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale on the width as no global locks or 
transactions has to be used, which with high probability would slow down the system, especially 
when widely distributed. 
The gain of having the locks or transactions would be that the system would always be
in a fully consistent state. The loss would be that all of the database nodes would need to 
constantly have to be fully aware of the state of the other nodes.

@@

>>>>

%}}}
\begin{abstract}
This work presents a technique for incorporating Copy-on-Write in a high level system on top of an
unaware persistent storage. The system in this case is a security management system, but the
technique and conclusions drawn are general enough to be applicable to any system with vaguely
similar consistency requirements. The scalability of the system is tested and the technique is
evaluated and the technique is shown to be quite efficient (scalable to >6000 simultaneous active
users per node), but a better solution is also suggested in the conclusion.\\

@@

\par
After adding indices, the building of the project tree was able to finish 50 times faster and the
server was able to serve 2100 requests/s, see Listing~\ref{INDEXREQUEST}. If using the same
approximated average that was used in connection to Listing~\ref{TREEREQUEST} (30 requests/s), the
maximum number of clients that one node can handle will be >60000, without taking the web servers
limits or content posting into consideration.

@@

\par
File uploads was not supported by WRK and therefore Apache Bench was used. As there is a lot of
difference depending on the hard drive and file system when benchmarking uploads which are greater
in size, which images usually are, no real conclusions can be drawn from this benchmark. It could
perform about 200 POSTS/second with an image of 200KB, but it's unsure if the server could
keep up that pace forever. If following the same example as earlier in the section with one POST per
user every 30 seconds that would make the system able to serve 6000 active users.

\newpage
\subsection{Security of the system}
\subsubsection{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius 
is mainly focussed at being deployed in internal networks which usually has an LDAP service enabled. 
LDAP also makes it easier for the user to login as no separate account is needed for Perius and 
thus the user can use the same account as for all the LDAP connected services on the internal 
network.

@@

\subsection{Copy-on-Write's effect on Scalability}
As no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from how its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale on the width as no global locks or 
transactions has to be used, which with high probability would slow down the system, especially 
when widely distributed. 
The gain of having the locks or transactions would be that the system would always be
in a fully consistent state. The loss would be that all of the database nodes would need to 
constantly have to be fully aware of the state of the other nodes.

@@

\subsection{GET/POST Estimation}
The estimation of 30 seconds/action that was made in Section~\ref{sec:load_testing} was only based
on observation, no logging of a system used in production (as no such system existed) could be made 
to back up that estimation. In the future those numbers can easily be recalculated, when there are
enough metrics from a fully deployed version of Perius.
